Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-06-25 reports/paper1/paper.tex

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[square,comma]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figurename=Fig.]{caption}
\usepackage[numbib]{tocbibind} %number references and figure title
\usepackage{authblk}

@@

\begin{abstract}
\noindent
\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
\newline
\textbf{OBJECTIVE}: It was investigated whether it is possible to detect defects based on a single angular projection, avoiding the time-consuming reconstruction process.
\newline
\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. To overcome imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
\newline
\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved.
\newline
\textbf{CONCLUSIONS}: Defect detection in projection space is possible. This work is a contribution towards real-time quality control in AM. The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter. Speeding up could be possible by implementing the filter on a GPU or exploring further robust estimators.
\newline
\newline
\emph{Keywords:} Additive manufacturing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
\end{abstract}

@@

Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control (CNC). In AM, the product is manufactured layer by layer to product complicated internal and external geometries \citep{ngo2018additive, wong2012review}. One common example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. Powder based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.

There is a need for product inspection, in particular quality assessment of the internal structures. The properties of materials produced by AM are not yet fully understood. For example, voids can form between layers which can impact the mechanical properties of the product \citep{ngo2018additive, wang20173d}. In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}. Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal deposits on the surface of the AM part. They are formed by sintered powder with insufficient contact on the existing layer \citep{gu2009balling, li2012balling}.

@@

An advantage of XCT is that the location of the pores can be visualised. Studies have shown a link between porosity and stress concentration \citep{carlton2016damage, leuders2015fatigue, siddique2015computed}. The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. In addition to pores, surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.

A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample. XCT is not a instantaneous process so progress bars are usually featured in marketing for XCT such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}. Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.

Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection. It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}. The simulated projections are made in software called \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test sample with purposely designed voids. An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using a black (\SI{0}{\kilo\volt}) and white image (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

The projection of the sample was obtained and repeated 20 times at a fixed angle. 19 randomly selected projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.

@@

We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect. It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel. A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result. Beforehand, the empirical null \citep{efron2004large} is used to locally normalisation \citep{sage2018local, sage2003teaching} the test statistics. This is necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

@@

It was assumed that the grey values were Normally distributed, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively with estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively. Define the null hypotheses
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
and the alternative hypotheses
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.

@@

Contamination was simulated by a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added. The null and alternative distributions are
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(\mu_{0,x,y}+2\mu_1,2^2)
\end{align}
respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. A simulated contaminated defected image was made by sampling $Z_{x,y}|H_{0,x,y}$ in areas with no defects and $Z_{x,y}|H_{1,x,y}$ with defects. An example of contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.

The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause an inflation in false positives.

It was suggested that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}. In this simulated example, it is about $r>\SI{54}{\pixel}$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

A simulation study was conducted where a simulated contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image. The area under the ROC curve (AUC) and statistical errors were recorded. This was repeated 100 times by simulating another image and repeating the measurement. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the AUC and errors without contamination.

@@

In the simulation study, defection detection was conducted on a uncontaminated defected image and a filtered contaminated defected image so that the statistical properties were compared. The results from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.

@@

It was observed that there is a kernel radius which minimised the type 2 error. A large kernel radius helped preserve false discovery rate (FDR) control after filtering in these examples but a kernel radius too large can lose statistical power. Keeping the FDR consistent before and after filtering is desirable so it is controlled at a specified level after filtering. For large enough kernel radius, the FDR was controlled at fluctuates around 5\%.

The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}. The running times are compared with the mean variance filter which normalise the statistics using the sample mean and sample standard deviation. Compared to the mean variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.

The resulting inference from the test sample is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}. The larger defects were successfully highlighted by the hypothesis test. The empirical null mean changed face to face, resulting in a clear boundary set by the edges. This suggest that the contamination or inaccuracy from \emph{aRTist} was face dependent.

@@

Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This can be extended to multiple projections and perhaps in real time on a conveyor belt.

The empirical null filter catered for inaccuracies made by \emph{aRTist}. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel. Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline. On the other hand, there are methods which uses the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature \citep{hampel1986robust, huber2009robust, jewson2018principles, maronna2006robust, rousseeuw1987robust}. The EM algorithm \citep{bishop2006pattern, dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean variance null filter}
      \end{subfigure}
    }
  \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image. The mean variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plots summarise the 100 repeated measurements of the running times.}
  \label{fig:inference_timing}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[square,numbers,comma]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figurename=Fig.]{caption}
\usepackage[numbib]{tocbibind} %number references and figure title
\usepackage{authblk}

@@

\begin{abstract}
\noindent
\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
\newline
\textbf{OBJECTIVE}: It was investigated whether it is possible to detect defects based on a single angular projection, avoiding the time-consuming reconstruction process.
\newline
\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
\newline
\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved.
\newline
\textbf{CONCLUSIONS}: Defect detection in projection space is possible. This work is a contribution towards real-time quality control in AM. The main bottleneck is the multiple evaluations of functions required for robust estimation in the empirical null filter. Speeding up could be possible by implementing the filter on a GPU or exploring further robust estimators.
\newline
\newline
\emph{Keywords:} Additive manufacturing, 3D printing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
\end{abstract}

@@

Additive manufacturing (AM) is an emerging technology that overcomes many traditional methods such as computer numerical control machining (CNC). In AM, the product is manufactured layer by layer to produce complicated internal and external geometries \citep{ngo2018additive, wong2012review}. One common example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in the form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. Powder-based AM such as selective laser sintering \citep{3d2019our, deckard1989method, dtm1990the} can manufacture metal products.

There is a need for product inspection, in particular, quality assessment of the internal structures. The properties of materials produced by AM are not yet fully understood. For example, voids can form between layers which can impact the mechanical properties of the product \citep{ngo2018additive, wang20173d}. In power-based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{tammas2015xct, thijs2010study}. Low wetting ability of the melt pool can cause balling, a phenomenon where spherical or ellipsoidal particles form on the surface of the AM part. They are formed by sintered powder with insufficient contact on the existing layer \citep{gu2009balling, li2012balling}.

@@

An advantage of XCT is that the location of the pores can be visualised. Studies have shown a link between porosity and stress concentration \citep{carlton2016damage, leuders2015fatigue, siddique2015computed}. The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. In addition to pores, the surface deviation can be measured by aligning the reconstruction with the computer-aided design (CAD) model and measuring any discrepancies \citep{kim2016inspection, lee2015compliance, villarraga2015assessing}.

A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample. XCT is not an instantaneous process so progress bars are usually featured XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}. Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.

Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection. It was demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without \citep{brierley2018optimized}. The simulated projections are made in software called \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. It is however inevitable that information is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test sample with purposely designed voids. An x-ray projection was obtained and compared with the simulated projection from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

X-ray projections were obtained using the \emph{Nikon XT H LC 225/320} x-ray CT scanner \emph{(Nikon Metrology, UK)}. The \SI{225}{\kilo\volt} source was used with a $\SI{2000}{\pixel}\times\SI{2000}{\pixel}$ \emph{Perkin Elmer} detector consisting of \SI{200}{\micro\metre} pixels, separated by a distance of \SI{1870}{\milli\metre}. The sample was placed on the manipulator, positioned to obtain a $5.7\times$ magnification resulting in an equivalent pixel size of \SI{35}{\micro\metre}. A voltage of \SI{80}{\kilo\volt} was used with a power of \SI{20}{\watt} resulting in a spot size of \SI{20}{\micro\metre} such that penumbra effects \citep{kueh2016modelling} were negligible. 20 greyscale projections were acquired at an exposure time of \SI{500}{\milli\second}. A shading correction \citep{munzenmayer2003enhancing, young2000shading} was applied to each projection using 20 black (\SI{0}{\kilo\volt}) and 20 white images (\SI{80}{\kilo\volt}) projection to remove intensity influences and variations in pixels of the detector.

19 randomly selected projections, of the test sample, were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2012radiographic, bellon2007artist, jaenisch2008artist}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. The same shading correction was applied to the simulated projection, but instead using a flat black image and a simulated white image.

@@

We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect. It is built on two-tailed multiple hypotheses testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate \citep{benjamini2010discovering, benjamini1995controlling}, conducting an individual test for each pixel. A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result. Beforehand, the empirical null \citep{efron2004large} is used to locally normalise \citep{sage2018local, sage2003teaching} the test statistics. This is necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

@@

It was assumed that the grey values were Normally distributed, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$. Their estimates, $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively, are called the empirical null mean and empirical null standard deviation. Define the null hypotheses
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
and the alternative hypotheses
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.

@@

Contamination was simulated by a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added. The null and alternative distributions are
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(\mu_{0,x,y}+2\mu_1,2^2)
\end{align}
respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. A simulated contaminated defected image was made by sampling $Z_{x,y}|H_{0,x,y}$ in areas with no defects and $Z_{x,y}|H_{1,x,y}$ with defects. An example of a contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.

The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause inflation in false positives.

It was suggested that, as a rule of thumb, the proportion of non-null statistics captured by the kernel should not be larger than $0.1$ to satisfy some assumptions made for the empirical null \citep{efron2004large, schwartzman2008empirical}. In this simulated example, it is about $r>\SI{54}{\pixel}$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

A simulation study was conducted where a simulated contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image. The area under the ROC curve (AUC) and statistical errors were recorded. This was repeated 100 times by simulating another image and repeating the measurement. To form a baseline to compare with, the results of the uncontaminated defected image were all pooled together to obtain the empirical distribution of the AUC and statistical errors without contamination.

@@

In the simulation study, defect detection was conducted on a filtered contaminated defected image to investigate the statistical properties of the method. The aim of the filter was to remove the contamination so that sensible inference was achieved. The results from the simulation is shown Fig.~\ref{fig:inference_Experiment_DefectRadiusSquare}.

@@

It was observed that there is a kernel radius which minimised the type 2 error. A large kernel radius helped preserve false discovery rate (FDR) control after filtering in these examples but a kernel radius too large can lose statistical power. Keeping the FDR consistent before and after filtering is desirable so it is controlled at a specified level after filtering. For large enough kernel radius, the FDR was controlled at and fluctuates around 5\%.

The running times of the filtering are shown in Fig.~\ref{fig:inference_timing}. The running times are compared with the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation. Compared to the mean-variance filter, the empirical null filter was slow and much slower for larger kernel radiuses.

The resulting inference from the test sample is shown in Fig.~\ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}. The larger defects were successfully highlighted by the hypothesis test. The empirical null mean changed face to face, resulting in a clear boundary set by the edges. This suggests that the contamination or inaccuracy from \emph{aRTist} was face dependent.

@@

Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This
work is a contribution towards real-time quality control in AM.

The empirical null filter catered for inaccuracies made by \emph{aRTist}. This demonstrated that the filter can adjust the null hypotheses according to the data to make a sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

@@

The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of each pixel in the kernel. Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however, that would require tuning the histogram bins as well as the tuning parameters for the spline. On the other hand, there are methods which use the histogram count and it was found that the estimation of the null parameters was insensitive to the histogram binning \citep{schwartzman2008empirical}.

Estimation of the null parameters is essentially robust statistics, estimating the parameters of the null distribution without being affected by non-null statistics. Potential faster methods than the empirical null could exist in literature \citep{hampel1986robust, huber2009robust, jewson2018principles, maronna2006robust, rousseeuw1987robust}. The EM algorithm \citep{bishop2006pattern, dempster1977maximum} could be used to fit a mixture of Gaussians to identify the null distribution and estimate its parameters. However, the power of hypothesis testing and the empirical null comes from the fact that the alternative distribution does not need to be specified.

@@

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianEmpirical_time.eps}
        \caption{Empirical null filter}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/AllNullGaussianMeanVar_time.eps}
        \caption{Mean-variance null filter}
      \end{subfigure}
    }
  \caption{Running times when filtering a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ image. The mean-variance null filter uses the sample mean and sample standard deviation to locally normalise the image. Note that the $y$-axis changes scale. The box plots summarise the 100 repeated measurements of the running times.}
  \label{fig:inference_timing}
\end{figure}
